\documentclass[12pt,onecolumn,letterpaper]{article}
\setcounter{secnumdepth}{5}

\title{dB Cafe Operations Manuel}
\author{HKN \& IEEE}
\date{ }

\begin{document}
\maketitle
\tableofcontents
\newpage

\section{Overview}

% ------------------------------------------------------------------------------
% ------------------------------------------------------------------------------
\section{Access to the dB Cafe}
The door to the dB Cafe will remain locked unless the space is being used activities related to the dB Cafe.

Keys to the dB Cafe can be found in the following locations:
\begin{enumerate}
\item Inside of the HKN Office
\item Inside of the IEE Office
\item On the HKN Operations Officer's person
\item On the HKN President's person
\end{enumerate}

% ------------------------------------------------------------------------------
% ------------------------------------------------------------------------------
\section{General Shifts: 8:30am - 4:30pm}
% ------------------------------------------------------------------------------
\subsection{Before}
The following actions must be preformed by any individual that is working a shift at the dB Cafe before starting their shift.
\begin{enumerate}
\item Arrive to your designated shift on time (not Michigan time)
\item Personal belongings must be place out of sight and not obstructing the working area
\item If you have long hair, use a hair tie or band to put your hair up. You may use a personal hair band or one of the ones provide
\item Wash your hands using the provided soap in the front sink following the pasted guidelines
\end{enumerate}
% ------------------------------------------------------------------------------
\subsection{During}
\subsubsection{Dos}
\begin{enumerate}
\item Use common sense
\item If you are unsure of something ask someone in 1226 EECS (the bullpen)
\item Keep the dB Cafe clean and organized
\item If it looks like trash, throw it out! (use the big trash bin)
\item Use the speakers to play music
\end{enumerate}
\subsubsection{Don'ts}
\begin{enumerate}
\item Eat or drink
\item Do homework
\item Dump anything down the front sink
\item Exchange money for change (we need our quarters)
\item Accept foreign money
\item Refund money used in vending machines
\item Accept tips
\end{enumerate}
\subsubsection{Sales Scanning}
All items sold at the dB Cafe must be tracked through the inventory system. 
\begin{enumerate}
\item When an item is sold, scan the barcode on the item with the provided barcode scanner
\item Some items do not have a barcode or the barcode is difficult to scan, in these cases, scan the custom printed barcode on the documents next to the scanner
\end{enumerate}
\subsubsection{Restocking}
Restock during down times throughout your shift and at the end of your shift. \textbf{Do not leave without restocking!}

When restocking a refrigerator restock from back to front. Place the new items in the back of the refrigerator while bringing older items to the front. This ensures that we sell older products before newer products.
\begin{description}
\item [Front Refrigerator] Use the pail to restock the front refrigerator with items from the back refrigerator
\item [Back Refrigerator] Restock the back refrigerator with items from the back shelves
\item [Coffee Accessories] Restock the lids, stir sticks, and creamers with items from the cabinets. If the cabinets are out of the item, check the back of the dB Cafe
\item [Glass Showcase] \textbf{Do not restock muffins or cookies.} Additional chips can be restocked from the back of the dB Cafe
\item [Candy Drawers] Restock the candy drawers from the candy boxes underneath the glass showcase 
\end{description}
% ------------------------------------------------------------------------------
\subsection{After}
\begin{enumerate}
\item Wait until replacement workers arrive before leaving, do not leave the dB Cafe unattended
\item If no replacement arrives and you need to leave, ask someone in 1226 EECS (the bullpen) for help
\end{enumerate}
% ------------------------------------------------------------------------------
% ------------------------------------------------------------------------------
\section{Special Shifts}
% ------------------------------------------------------------------------------
\subsection{Pizza Shifts: 11:30am - 2:30pm}
The following actions must be preformed by any individual that is working a Pizza shift at the dB Cafe.
\subsubsection{Setting Up Pizza Boxes}
\begin{enumerate}
\item When pizza is delivered, place the the pizza bags on the back shelf and pay the delivery person. 
	\begin{enumerate}
	\item If the delivery person tells you the amount owed including tip, pay them that amount
	\item If the delivery person tells you the amount owed \textbf{not} including tip, then pay them the amount owed + 10\% tip rounded up to the nearest 5 dollars.
	\end{enumerate}
\item Using a marker from the money drawer, label each box with the initial corresponding to the type of pizza. This makes it easier to tell which type of pizza is in each box
\item Using pizza boxes from previous shifts and the pizza boxes that just arrived, ensure that there is exactly:
	\begin{enumerate}
	\item one box of Cheese, Mushroom, Spinach Alfredo, and the Weekly Special pizza on top of the shelf above the back counter
	\item one box of Pepperoni, Bacon, Sausage, and BBQ Chicken pizza on top of the pizza bags on the back counter
	\end{enumerate}
\item Close the pizza bags when you are finished moving pizza boxes
\end{enumerate}
\subsubsection{Selling Pizza}
\begin{enumerate}
\item Take a plate and napkin over the pizza boxes
\item Use the napkin to remove the pizza from the box and put it on the plate.
\item \textbf{Never touch the pizza with your hands}
\item Make sure to close the pizza box when you are finished
\item If a pizza box runs out of slices:
	\begin{enumerate}
	\item Stack the pizza boxes by the door of the dB Cafe
	\item Do not stack pizza boxes above the sign that reads "Do not Stack Boxes Above This Point"
	\item Take a replacement pizza box out of the pizza bag and put it on the shelf
	\item If there is not a replacement pizza, using a dry erase marker from the money drawer cross off the type of pizza from the menu
	\end{enumerate}
\end{enumerate}
% ------------------------------------------------------------------------------
\subsection{Opening Shift: 8:00am - 8:30am}
The following actions must be preformed by any individual that is opening the dB Cafe.

Steps 1 \& 2 must be preformed before any of the remaining steps.
\begin{enumerate}
\item Plug in the coffee maker
\item Retrieve the toaster slide from the drying rack in the back of the dB Cafe, attach it to the toaster, and plug in the toaster 
\item Retrieve the bags of bagels from outside of the dB Cafe door, roll down the bags, and place the bags in/above the correct bins
\item Retrieve muffin boxes (1 of each type of muffin) from the back shelves, and place them in the display case
\item Retrieve the bagel cutters, coffee pots, coffee scoop, and funnel from the drying rack in the back room.
\item Take 3 rolls of quarters and the stack of bills out of the safe in the back room, and neatly place them in the money drawer in the front.
\item Turn on the dB Cafe neon sign and ring light
\item Unlock the locks on both sides of the gate, and open the gate at 8:30am sharp
\end{enumerate}
% ------------------------------------------------------------------------------
\subsection{Closing Shift: 4:30pm - 2:30pm}

% ------------------------------------------------------------------------------
% ------------------------------------------------------------------------------
\section{Food Serving Guidelines}
% ------------------------------------------------------------------------------
\subsection{Making Coffee}
% ------------------------------------------------------------------------------
\subsection{Tea \& Hot Chocolate}
% ------------------------------------------------------------------------------
\subsection{Raman}

% ------------------------------------------------------------------------------
% ------------------------------------------------------------------------------
\section{Treasurer Duties}
This individual is prohibited from working a shift at the dB Cafe excluding the opening or closing shift. They are prohibited form accepting money from customers. 
% ------------------------------------------------------------------------------
\subsection{Daily money counting}
The following actions must be preformed by the treasurer of HKN at 4:30pm daily. 
\begin{enumerate}
\item To determine the day's revenue, count all of the bills in the money drawer and remove the daily starting amount
\item Place the daily revenue into the revenue folder and place it in the HKN safe
\item Place the daily starting amount into the dB Cafe safe
\end{enumerate}
% ------------------------------------------------------------------------------
\subsection{Weekly bank deposits}
The following actions must be preformed by the treasurer of HKN on a weekly basis.
\begin{enumerate}
\item Take the weekly dB Cafe revenue money from the HKN safe and deposit it into the dB Cafe bank account at the UM Credit Union.
\end{enumerate}

% ------------------------------------------------------------------------------
% ------------------------------------------------------------------------------
\section{Restocking the dB Cafe}
//Insert steps for db runs
\end{document}